Les besoins en éducation pour les pratiques opensource

### 2022-06-10 main.tex
Improve english and glossary helper commands
fix a very little kaobook oversight
update kaobook
progress the lit. review and glossary
kabiblio: fix the repeating information in margin citations
bib: do not write family names in small caps
csquotes: automatically use french style guillemets
compilation: silence a spurious warning

% Suppress some compilation warnings
\RequirePackage[save,showerrors]{silence}
\WarningFilter{biblatex}
  {The starred command '\DeclareDelimAlias*' is} % APA package is using this deprecated starred version
\WarningFilter{transparent}
  {Loading aborted} % I can't find where it is loaded, probably somewhere in kao's cls or sty
\WarningFilter{latex}
  {Unused global option} % They are, but kaobook is silently passing them to its base class

@@

% Main and default language is french but there are some parts in english
\usepackage[main=french,english]{babel}
\newcommand{\english}[1]{\foreignlanguage{english}{\itshape #1}}
\usepackage{csquotes}

@@

% Bibliography configuration
\usepackage[style=apa]{kaobiblio}
\addbibresource{references.bib}

@@

% Configure the index and the glossary
\makeindex[columns=3, title=Alphabetical Index, intoc]
\makeglossaries
\input{glossary}

>>>>

% Suppress some compilation warnings
\RequirePackage[save,showerrors]{silence}
\WarningFilter{biblatex}
  {The starred command '\DeclareDelimAlias*' is} % APA package is using this deprecated starred version
\WarningFilter{transparent}
  {Loading aborted} % I can't find where it is loaded, probably somewhere in kao's cls or sty
\WarningFilter{latex}
  {Unused global option} % They are, but kaobook is silently passing them to its base class
\WarningFilter{latex}
  {Marginpar on page} % Margin stuff moved to not overlap with other stuff, this is fine
\WarningFilter{latex}
  {There were undefined references} % seems spurious, no undefined references are reported
\WarningFilter{biblatex}
  {Please (re)run Biber on the file} % linked to the previous warning

@@

% Main and default language is french but there are some parts in english
\usepackage[main=french,english]{babel}
\newcommand{\en}[1]{\foreignlanguage{english}{\itshape #1}}
\usepackage{csquotes}
\MakeOuterQuote{"}

@@

% Bibliography configuration
\usepackage[style=apa]{kaobiblio}
\DefineBibliographyExtras{french}{\restorecommand\mkbibnamefamily}
\addbibresource{references.bib}

@@

% Configure the index and the glossary
\makeindex[columns=3, title=Alphabetical Index, intoc]
\makeglossaries
\setglossarystyle{altlist} % TODO: switch to altlistgroup if I end up with a lot entries
\input{glossary}
% shortcut for english glossary entries
\newcommand{\engl}[1]{\en{\gls{#1}}}
\newcommand{\enGl}[1]{\en{\Gls{#1}}}
\newcommand{\englpl}[1]{\en{\glspl{#1}}}
\newcommand{\enGlpl}[1]{\en{\Glspl{#1}}}
